Network Data Model and BerlinMOD Benchmark

### 2010-07-09 Algebras/Network/BerlinMODNetwork/paper/PaperBerlinMODAndNetworkDataModel.tex
Added Appendix Network Queries

The operation \op{mgpoint2mpoint} is described by Algorithm
\ref{alg:mgpoint2mpoint}. The loop from line 3 to line 28 is repeated $m$ times. The statements from
line 5 to line 8 take O($\log R + l_i$) every time they are executed. But they
are only executed at the first run of the loop and if the car changes the route.
We have three different cases for the computing of the $mpoint$ units. The
simple cases from line 10-11 and line 13-16 have a time complexity of O(1).
The third case has a worst case complexity from O($l_i$). The last line 29 has a time
complexity of O($m_{res}$) if $m_{res}$ is the number of units of the resulting
\dt{mpoint} value. In the worst case we get a time complexity of
\[O(m \log {R} + \sum_{i=1}^{m}{l_i} + m_{res}).\]
\begin{algorithm}[H]
  \caption{\op{mgpoint2mpoint}($mgp$)}
  \label{alg:mgpoint2mpoint}
  \begin{algorithmic}[1]
    \STATE $actRID$ = -1
    \STATE Initialize resulting $mpoint$
    \FOR{each unit $curUGP$ of $mgp$}
      \IF{not (rid from $curUGP$ == $actRID$)}
        \STATE $actRID$ = rid from $curUGP$
        \STATE $rc$ = route curve of $actRID$
        \COMMENT{$rc$ determined using B-Tree Index of $routes$ relation}
        \STATE Perform binary search on the line segments of $rc$ to find
        line segment $l$ with start position of $curUGP$
        \STATE $upstart$ = x,y-coordinates of start position
      \ENDIF
      \IF{end position == start position}
        \STATE add unit $upstart,\ upstart$ to $mpoint$
      \ELSE
        \IF{end position is on $l$}
          \STATE $upend$ = x,y-coordinates of end position
          \STATE add unit $upstart,\ upend$ to $mpoint$
          \STATE $upstart$ = $upend$
        \ELSE
          \STATE Follow $rc$ in moving direction of $curUGP$
          \WHILE{not(end position is on $l$)}
            \STATE add unit from $upstart$ to $segment\ end\ position$ to
$mpoint$
            \STATE $upstart$ = $segment\ end\ position$
            \STATE $l$ = next segment in moving direction
          \ENDWHILE
          \STATE $upend$ = x,y-coordinates of end position
          \STATE add unit from $upstart$ to $upend$ to $mpoint$
        \ENDIF
      \ENDIF
    \ENDFOR
    \RETURN $mpoint$
  \end{algorithmic}
\end{algorithm}

In the trip based approach (TBA) the result values of the different trips must be
aggregated to an single result value. Therefore the operation \op{union} was
introduced. \op{union} gets two \dt{gline} values or two \dt{mgpoint} values as
input and mixes them up to a single sorted \dt{gline} or a single \dt{mgpoint}
value.
\begin{tabbing}
xxxxxxxxxxxxxxxxxxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx\kill
\dt{gline} $\times$ \dt{gline} $\rightarrow$ \dt{gline} \> $gline1$ \op{union} $gline2$ \\
\dt{mgpoint} $\times$ \dt{mgpoint} $\rightarrow$ \dt{mgpoint} \> $mgpoint1$ \op{union} $mgpoint2$\\
\end{tabbing}
\begin{algorithm}[H]
  \caption{\op{union}($gl_1$, $gl_2$)}
  \label{alg:uniongline}
  \begin{algorithmic}
    \IF{$gl_1$ is sorted AND $gl_2$ is sorted}
      \STATE Perform parallel scan of $gl_1$ and $gl_2$
      \IF{Current $route\ intervals$ do not intersect}
         \STATE Add smaller $route\ interval$ to result
         \STATE Continue Scan with next $route\ interval$
      \ELSE
          \STATE Merge $route\ intervals$ into one
          \IF{Next $route\ intervals$ intersect the merged one}
            \STATE merge them too
          \ENDIF
          \STATE Add merged $route\ interval$ to result
          \STATE Continue Scan
      \ENDIF
    \ELSE
      \FOR{Each $route\  interval$ of $gl_1$ and $gl_2$}
        \STATE Insert $route\ interval$ into $RITree$
      \ENDFOR
      \STATE Copy sorted $route\ intervals$ from $RITree$ to resulting \dt{gline}
    \ENDIF
    \RETURN resulting \dt{gline}
  \end{algorithmic}
\end{algorithm}
The Algorithm \ref{alg:uniongline} distinguishes between two cases.
If both \dt{gline} values are sorted the algorithm has a time complexity of
O($r_1 + r_2$) and if one or both \dt{gline} are not sorted it has a time
complexity of O($(r_1 + r_2) \log r_{res} + r_{res}$), if $r_{res}$ is the
number of $route\ intervals$ of the resulting \dt{gline}. The additional
time results from sorting and compressing the resulting $route\ intervals$. As
explained before (see Section \ref{sec:implNetDataTyp}) we think that this time
is well invested, because several algorithms take profit from sorted \dt{gline}
values.

@@

\>\>\>\op{project} [Licence, Model]\\

@@

\>\>\>\op{loopjoin}[dataMNtrip\_Moid\_btree dataMNtrip \op{exactmatch}[.Moid\_ll]]\\

@@

\>\>\op{projectextend}[Instant\_i, Licence\_ll; Pos: \op{val}(.Trip \op{atinstant} .Instant\_i)]\\

@@

\>\op{symmjoin}[(.Box\_a \op{intersects} ..Box\_b) \op{and} (.Licence\_a < ..Licence\_b) \op{and}\\

@@

\>dataMcar \op{feed filter} [.Type = ''truck''] \op{project} [Licence, Moid] \{c\}\\

@@

\>\>\>\op{filter}[.Type = "passenger"]\\

@@

\>\op{filter}[.Type = "passenger"]\\

@@

\>\op{filter}[.Instant <= .FirstTime\_b]\\

@@

\>\op{filter}[.TimeAtPos\_a <= .FirstTime\_b]\\

@@

\end{tabbing}
\end{scriptsize}
\end{document}

>>>>

The operation \op{mgpoint2mpoint} is described by Algorithm
\ref{alg:mgpoint2mpoint}. The loop from line 3 to line 28 is repeated $m$ times. The statements from
line 5 to line 8 take O($\log R + l_i$) every time they are executed. But they
are only executed at the first run of the loop and if the car changes the route.
We have three different cases for the computing of the $mpoint$ units. The
simple cases from line 10-11 and line 13-16 have a time complexity of O(1).
The third case has a worst case complexity from O($l_i$). The last line 29 has a time
complexity of O($m_{res}$) if $m_{res}$ is the number of units of the resulting
\dt{mpoint} value. In the worst case we get a time complexity of
\[O(m \log {R} + \sum_{i=1}^{m}{l_i} + m_{res}).\]
  \caption{\op{mgpoint2mpoint}($mgp$)}
  \label{alg:mgpoint2mpoint}
    \STATE $actRID$ = -1
    \STATE Initialize resulting $mpoint$
    \FOR{each unit $curUGP$ of $mgp$}
      \IF{not (rid from $curUGP$ == $actRID$)}
        \STATE $actRID$ = rid from $curUGP$
        \STATE $rc$ = route curve of $actRID$
        \COMMENT{$rc$ determined using B-Tree Index of $routes$ relation}
        \STATE Perform binary search on the line segments of $rc$ to find
        line segment $l$ with start position of $curUGP$
        \STATE $upstart$ = x,y-coordinates of start position
      \ENDIF
      \IF{end position == start position}
        \STATE add unit $upstart,\ upstart$ to $mpoint$
      \ELSE
        \IF{end position is on $l$}
          \STATE $upend$ = x,y-coordinates of end position
          \STATE add unit $upstart,\ upend$ to $mpoint$
          \STATE $upstart$ = $upend$
        \ELSE
          \STATE Follow $rc$ in moving direction of $curUGP$
          \WHILE{not(end position is on $l$)}
            \STATE add unit from $upstart$ to $segment\ end\ position$ to
$mpoint$
            \STATE $upstart$ = $segment\ end\ position$
            \STATE $l$ = next segment in moving direction
          \ENDWHILE
          \STATE $upend$ = x,y-coordinates of end position
          \STATE add unit from $upstart$ to $upend$ to $mpoint$
        \ENDIF
      \ENDIF
    \RETURN $mpoint$
In the trip based approach (TBA) the result values of the different trips must
be
aggregated to an single result value. Therefore the operation \op{union} was
introduced. \op{union} gets two \dt{gline} values or two \dt{mgpoint} values as
input and mixes them up to a single sorted \dt{gline} or a single \dt{mgpoint}
value.
\dt{gline} $\times$ \dt{gline} $\rightarrow$ \dt{gline} \> $gline1$ \op{union} $gline2$ \\
\dt{mgpoint} $\times$ \dt{mgpoint} $\rightarrow$ \dt{mgpoint} \> $mgpoint1$ \op{union} $mgpoint2$\\
  \caption{\op{union}($gl_1$, $gl_2$)}
  \label{alg:uniongline}
  \begin{algorithmic}
    \IF{$gl_1$ is sorted AND $gl_2$ is sorted}
      \STATE Perform parallel scan of $gl_1$ and $gl_2$
      \IF{Current $route\ intervals$ do not intersect}
         \STATE Add smaller $route\ interval$ to result
         \STATE Continue Scan with next $route\ interval$
      \ELSE
          \STATE Merge $route\ intervals$ into one
          \IF{Next $route\ intervals$ intersect the merged one}
            \STATE merge them too
          \ENDIF
          \STATE Add merged $route\ interval$ to result
          \STATE Continue Scan
      \ENDIF
    \ELSE
      \FOR{Each $route\  interval$ of $gl_1$ and $gl_2$}
        \STATE Insert $route\ interval$ into $RITree$
      \STATE Copy sorted $route\ intervals$ from $RITree$ to resulting \dt{gline}
    \ENDIF
    \RETURN resulting \dt{gline}
The Algorithm \ref{alg:uniongline} distinguishes between two cases.
If both \dt{gline} values are sorted the algorithm has a time complexity of
O($r_1 + r_2$) and if one or both \dt{gline} are not sorted it has a time
complexity of O($(r_1 + r_2) \log r_{res} + r_{res}$), if $r_{res}$ is the
number of $route\ intervals$ of the resulting \dt{gline}. The additional
time results from sorting and compressing the resulting $route\ intervals$. As
explained before (see Section \ref{sec:implNetDataTyp}) we think that this time
is well invested, because several algorithms take profit from sorted \dt{gline}
values.

@@

@@

\>\>\op{loopjoin}[dataMNtrip\_Moid\_btree dataMNtrip
\op{exactmatch}[.Moid\_ll]]\\

@@

\>\op{projectextend}[Instant\_i, Licence\_ll; Pos: \op{val}(.Trip
\op{atinstant} .Instant\_i)]\\

@@

\>\op{symmjoin}[(.Box\_a \op{intersects} ..Box\_b) \op{and} (.Licence\_a $<$
..Licence\_b) \op{and}\\

@@

\>dataMcar \op{feed filter} [.Type = 'truck'] \op{project} [Licence, Moid]
\{c\}\\

@@

\>\>\>\op{filter}[.Type = 'passenger']\\

@@

\>\op{filter}[.Type = 'passenger']\\

@@

\>\op{filter}[.Instant $\leq$ .FirstTime\_b]\\

@@

\>\op{filter}[.TimeAtPos\_a $\leq$ .FirstTime\_b]\\

@@

\op{let} Q8OBA =\\
\>\>\op{loopsel} [dataSNcar\_Licence\_btree dataSNcar \op{exactmatch}
[.Licence\_l]]\\
\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))] \{p\}\\
\>\op{projectextend} [Licence, Period\_p; Distance: \op{length}(.Trip
\op{atperiods} .Period\_p)]\\
\op{let} Q8TBA =\\
\>\>\op{loopjoin}[dataMcar\_Licence\_btree dataMcar
\op{exactmatch}[.Licence\_l]]\\
\>\>\op{project}[Licence, Moid]\\
\>\>\op{loopsel}[\op{fun} (t:TUPLE) dataMNtrip\_Moid\_btree dataMNtrip
\op{exactmatch}[attr(t, Moid)]\\
\>\>\>\op{projectextend}[Trip; Licence: attr(t,Licence)]]\\
\>QueryPeriods1 \op{feed}\\
\>\op{symmjoin} [.Trip \op{present} ..Period]\\
\>\op{projectextend} [Licence, Period, Id; Distance: \op{length}(.Trip
\op{atperiods} .Period)]\\
\>\op{sortby} [Id \op{asc}, Licence \op{asc}, Distance \op{desc}]\\
\>\op{groupby}[Id, Period, Licence; Dist: \op{group feed sum}[Distance]]\\
\>\op{project}[Licence, Period, Dist]\\
\op{let} Q9OBA =\\
\>dataSNcar \op{feed} \{c\}\\
\>QueryPeriods \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\op{projectextend} [Id\_p, Period\_p, Licence\_c; Dist: \op{length}(.Trip\_c
\op{atperiods} .Period\_p)]\\
\>\op{sortby} [Id\_p \op{asc}, Period\_p \op{asc}, Dist \op{desc}]\\
\>\op{groupby} [Id\_p, Period\_p; Distance: \op{group feed max}[Dist]]\\
\>\op{project} [Id\_p, Period\_p, Distance]\\
\>\op{sortby} [Id\_p \op{asc}]\\
\>\op{project} [Period\_p, Distance]\\
\op{let} Q9TBA =\\
\>dataMNtrip \op{feed} \{c\}\\
\>QueryPeriods \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\op{symmjoin}[.Trip\_c \op{present} ..Period\_p]\\
\>\op{projectextend} [Moid\_c, Period\_p, Id\_p; Distance: \op{length}(.Trip\_c
\op{atperiods} .Period\_p)]\\
\>\op{sortby} [Id\_p \op{asc}, Moid\_c \op{asc}, Distance \op{desc}]\\
\>\op{groupby} [Id\_p, Period\_p, Moid\_c; Dist: \op{group feed
sum}[Distance]]\\
\>\op{groupby}[Id\_p, Period\_p; Dista: \op{group feed max}[Dist]]\\
\>\op{project}[Period\_p, Dista]\\
\op{let} Q10OBA =\\
\>dataSNcar \op{feed}\\
\>\>\op{projectextend}[Licence; TripA: \op{mgpoint2mpoint}(.Trip), BBox:
\op{mgpbbox}(.Trip)]\\
\>\>\op{projectextend}[Licence, TripA; Box: \op{rectangle2}((\op{minD}(.BBox,1)
- 1.5), (\op{maxD}(.BBox,1) + 1.5),\\
\>\>\>\>(\op{minD}(.BBox,2) - 1.5), (\op{maxD}(.BBox,2) + 1.5))]\{c1\}\\
\>QueryLicences1 \op{feed}\\
\>\>\op{loopsel}[dataSNcar\_Licence\_btree dataSNcar
\op{exactmatch}[.Licence]]\\
\>\>\op{projectextend}[Licence, Trip;  BBox: \op{mgpbbox}(.Trip)]\\
\>\>\op{projectextend}[Licence, Trip; TripA: \op{mgpoint2mpoint}(.Trip), Box:
\op{rectangle2}(\op{minD}(.BBox,1) - 1.5),\\
\>\>\>\>(\op{maxD}(.BBox,1) + 1.5), (\op{minD}(.BBox,2) - 1.5),
(\op{maxD}(.BBox,2) + 1.5))] \{c2\}\\
\>\op{symmjoin}[.Box\_c1 \op{intersects} ..Box\_c2]\\
\>\op{filter} [.Licence\_c1 $\neq$ .Licence\_c2]\\
\>\op{filter} [\op{everNearerThan}(.TripA\_c1, .TripA\_c2, 3.0)]\\
\>\op{projectextend} [Licence\_c1, Licence\_c2; \\
\>\>\>\>Pos: .Trip\_c2 \op{atperiods deftime}((\op{distance}(.TripA\_c1,
.TripA\_c2) $<$ 3.0) \op{at} \true{}]\\
\>\op{filter} [\op{not}(\op{isempty}(.Pos))]\\
\>\op{project} [Licence\_c2, Licence\_c1, Pos]\\
\>\op{sortby} [Licence\_c2 \op{asc}, Licence\_c1 \op{asc}]\\
\op{let} Q10TBA =\\
\>QueryLicences1 \op{feed project}[Licence] \{V1\}\\
\>\op{loopsel}[\op{fun} (t:TUPLE) dataMcar\_Licence\_btree dataMcar
\op{exactmatch}[attr(t,Licence\_V1)]\\
\>\>\op{project}[Moid]\\
\>\>\op{loopjoin}[dataMNtrip\_Moid\_btree dataMNtrip
\op{exactmatch}[.Moid] \op{remove}[Moid]] \{V3\}\\
\>\>\op{extend}[t3bbx: \op{mgpbbox}(.Trip\_V3)]\\
\>\>\op{extend}[ptripA: \op{mgpoint2mpoint}(.Trip\_V3)]\\
\>\>\op{loopjoin}[\op{fun} (u:TUPLE) dataMNtrip\_SpatioTemp
\op{windowintersectsS}[\op{rectangle3}(\\
\>\>\>\>\op{minD}(attr(u,t3bbx),1) - 3.0, \op{maxD}(attr(u,t3bbx),1) + 3.0,\\
\>\>\>\>\op{minD}(attr(u,t3bbx),2) - 3.0, \op{maxD}(attr(u,t3bbx),2) + 3.0,\\
\>\>\>\>\op{minD}(attr(u,t3bbx),3), \op{maxD}(attr(u,t3bbx),3))]\\
\>\>\>\op{sort rdup} dataMNtrip \op{gettuples}\\
\>\>\>\op{filter} [.Moid $\neq$ attr(u, Moid\_V3)]\\
\>\>\>\op{projectextend} [Moid; ptripB: \op{mgpoint2mpoint}(.Trip)]\\
\>\>\>\op{filter} [\op{everNearerThan}(attr(u, ptripA), .ptripB, 3.0)]\\
\>\>\>\op{projectextend}[Moid; Times: \op{deftime}((\op{distance}(attr(u,
ptripA), .ptripB) $<$ 3.0) \op{at} \true{})]\\
\>\>\>\op{filter}[\op{not}(\op{isempty}(.Times))]\\
\>\>\>\op{loopjoin}[dataMcar\_Moid\_btree dataMcar
\op{exactmatch}[.Moid] \op{project}[Licence]]]\\
\>\>\op{projectextend}[Times, Trip\_V3; QueryLicence: attr(t,Licence\_V1),
OtherLicence: .Licence]\\
\>\>\op{projectextend}[QueryLicence, OtherLicence; Pos: .Trip\_V3
\op{atperiods} .Times]\\
\>\>\op{filter}[\op{not}(\op{isempty}(.Pos))]]\\
\>\op{sortby}[QueryLicence \op{asc}, OtherLicence \op{asc}]\\
\>\op{groupby}[QueryLicence, OtherLicence; AllPos: \op{group feed}\\
\>\>\>\op{aggregateB}[Pos; \op{fun} (M1:mgpoint, M2:mgpoint) M1 \op{union} M2;
[const mgpoint value()]]]\\
\>\op{project}[QueryLicence, OtherLicence, AllPos]\\
\op{let} Q11bOBA =\\
\>QueryPoints1Net \op{feed projectextend}[Id, Pos; Prect:
\op{gpoint2rect}(.Pos)]\{p\}\\
\>\op{projectextend}[Id\_p, Instant\_i; Box: \op{box3d}(.Prect\_p,
.Instant\_i)]\\
\>\op{loopsel}[\op{fun}(t:TUPLE) dataSNcar\_BoxNet\_timespace
\op{windowintersectsS}[attr(t,Box)]\\
\>\>\op{sort rdup} dataSNcar \op{gettuples}\\
\>\>\op{projectextend} [Licence; Id: attr(t,Id\_p), Instant\_i:
attr(t,Instant\_i)]]\\
\op{let} Q11TBA =\\
\>QueryPoints1Net \op{feed projectextend}[Id, Pos; Prect:
\op{gpoint2rect}(.Pos)]\{p\}\\
\>\op{loopsel}[\op{fun} (t:TUPLE) dataMNtrip\_BoxNet\_timespace
\op{windowintersectsS}[\\
\>\>\>\op{box3d}(attr(t,Prect\_p), attr(t,Instant\_i))]\\
\>\>\op{sort rdup} dataMNtrip \op{gettuples}\\
\>\>\op{projectextend}[Moid; Id: attr(t,Id\_p), Instant:
attr(t,Instant\_i)]]\{a\}\\
\>\op{loopjoin}[dataMcar\_Moid\_btree dataMcar \op{exactmatch}[.Moid\_a]]\\
\>\op{project}[Id\_a, Instant\_a, Licence]\\
\>\op{sortby} [Id\_a \op{asc}, Instant\_a \op{asc}, Licence \op{asc}]\\
\>\op{krdup} [Id\_a, Instant\_a, Licence]\\
\op{let} Q12hOBA =\\
\>QueryPoints1Net \op{feed projectextend}[Id, Pos; Prect:
\op{gpoint2rect}(.Pos)]\{p\}\\
\>\op{loopsel}[ \op{fun} (t:TUPLE) dataSNcar\_BoxNet\_timespace
windowintersectsS[\\
\>\>\>\op{box3d}(attr(t,Prect\_p), attr(t,Instant\_i))]\\
\>\>\op{sort rdup} dataSNcar \op{gettuples}\\
\>\>\op{projectextend} [Licence; Id\_p: attr(t,Id\_p), Pos\_p: attr(t,Pos\_p),
Instant\_i: attr(t,Instant\_i)]]\\
\>\op{sortby} [Id\_p \op{asc}, Instant\_i \op{asc}, Licence \op{asc}]\\
\op{let} Q12OBA =\\
\>Q12hOBA \op{feed} \{c1\}\\
\>Q12hOBA \op{feed} \{c2\}\\
\>\op{symmjoin} [(.Licence\_c1 $<$ ..Licence\_c2) \op{and} (.Id\_p\_c1 =
..Id\_p\_c2) \op{and} (.Instant\_i\_c1 = ..Instant\_i\_c2)]\\
\>\op{project} [Id\_p\_c1, Pos\_p\_c1, Instant\_i\_c1, Licence\_c1,
Licence\_c2]\\
\>\op{sortby} [Id\_p\_c1 \op{asc}, Instant\_i\_c1 \op{asc}, Licence\_c2
\op{asc}]\\
\op{delete} Q12hOBA;\\
\op{let} Q12hTBA =\\
\>QueryPoints1Net \op{feed projectextend}[Id, Pos; Prect:
\op{gpoint2rect}(.Pos)]\{p\}\\
\>\op{projectextend} [Id\_p, Pos\_p, Instant\_i; Box: \op{box3d}(.Prect\_p,
.Instant\_i)]\\
\>\op{loopsel}[\op{fun} (t:TUPLE) dataMNtrip\_BoxNet\_timespace
\op{windowintersectsS}[attr(t,Box)]\\
\>\>\op{sort rdup} dataMNtrip \op{gettuples}\\
\>\>\op{projectextend}[Moid; Id: attr(t,Id\_p), Instant:
attr(t,Instant\_i)]]\{a\}\\
\>\op{loopjoin}[dataMcar\_Moid\_btree dataMcar \op{exactmatch}[.Moid\_a]]\\
\>\op{projectextend}[Moid, Licence; Id: .Id\_a, Instant: .Instant\_a]\\
\op{let} Q12TBA =\\
\>Q12hTBA \op{feed} \{A\}\\
\>Q12hTBA \op{feed} \{B\}\\
\>\op{symmjoin} [(.Id\_A = ..Id\_B) \op{and} (.Instant\_A = ..Instant\_B) \op
{and} (.Moid\_A $<$ ..Moid\_B)]\\
\>\op{project} [Id\_A, Instant\_A, Licence\_A, Licence\_B]\\
\>\op{sortby} [Id\_A \op{asc}, Instant\_A \op{asc}, Licence\_B \op{asc}]\\
\op{delete} Q12hTBA;\\
\op{let} Q13OBA =\\
\>dataSNcar \op{feed} \{c\}\\
\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))] \{r\}\\
\>\op{symmjoin}[.Trip\_c \op{passes} ..Region\_r]\\
\>\op{projectextend}[Licence\_c, Id\_r, Region\_r; Trip: .Trip\_c \op{at}
.Region\_r]\\
\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\op{symmjoin} [.Trip \op{present} ..Period\_p]\\
\>\op{projectextend}[Id\_r, Period\_p; Licence: .Licence\_c, Trip: .Trip
\op{atperiods} .Period\_p]\\
\>\op{filter} [\op{no\_components}(.Trip) $>$ 0]\\
\>\op{project} [Id\_r, Period\_p, Licence]\\
\>\op{sortby} [Id\_r \op{asc}, Period\_p \op{asc}, Licence \op{asc}]\\
\op{let} Q13TBA =\\
\>dataMNtrip \op{feed} \{c\}\\
\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))] \{r\}\\
\>\op{symmjoin}[.Trip\_c \op{passes} ..Region\_r]\\
\>\op{projectextend}[Moid\_c, Id\_r; Trip: .Trip\_c \op{at} .Region\_r]\\
\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\op{symmjoin}[.Trip \op{present} ..Period\_p]\\
\>\op{loopjoin} [dataMcar\_Moid\_btree dataMcar exactmatch[.Moid\_c]]\\
\>\op{project}[Licence, Id\_r, Period\_p]\\
\>\op{sortby} [Id\_r \op{asc}, Period\_p \op{asc}, Licence \op{asc}]\\
\>\op{krdup} [Id\_r, Period\_p, Licence]\\
\op{let} Q14OBA =\\
\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))]\\
\>\op{projectextendstream}[Id, Region; Rrect:  \op{routeintervals}(.Region)]
\{r\}\\
\>{product}\\
\>\op{projectextend}[Id\_R, Region\_r, Instant\_i; Box:
\op{box3d}(attr(t,Rrect\_r), attr(t,Instant\_i))]\\
\>\op{loopsel}[\op{fun} (t:TUPLE) dataSNcar\_BoxNet\_timespace
\op{windowintersectsS}[attr(t,Box)]\\
\>\>\op{sort rdup} dataSNcar \op{gettuples}\\
\>\>\op{filter}[(\op{val}(.Trip \op{atinstant} (attr(t,Instant\_i))))
\op{inside} (attr(t,Region\_r))]\\
\>\>\op{projectextend} [Licence;Instant: attr(t,Instant\_i), Id:
attr(t,Id\_r)]]\\
\>\op{sortby} [Id \op{asc}, Instant \op{asc}, Licence \op{asc}]\\
\>\op{krdup}[Id, Instant, Licence]\\
\op{let} Q14TBA =\\
\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))]\\
\>\>\op{projectextendstream}[Id, Region; Brect:
\op{routeintervals}(.Region)]\{r\}\\
\>\op{projectextend}[Id\_r, Region\_r, Instant\_i; Box: \op{box3d}(.Brect\_r,
.Instant\_i)]\\
\>\op{loopsel}[ \op{fun} (t:TUPLE) dataMNtrip\_BoxNet\_timespace
\op{windowintersectsS}[attr(t,Box)]\\
\>\>\op{sort rdup} dataMNtrip \op{gettuples}\\
\>\>\op{filter}[(\op{val}(.Trip \op{atinstant} (attr(t,Instant\_i))))
\op{inside} (attr(t,Region\_r))]\\
\>\>\op{projectextend}[Moid;Instant: attr(t,Instant\_i), Id:
attr(t,Id\_r)]]\{a\}\\
\>\op{loopjoin}[dataMcar\_Moid\_btree dataMcar exactmatch [.Moid\_a]]\\
\>\op{projectextend}[Licence; Id: .Id\_a, Instant: .Instant\_a]\\
\>\op{sortby} [Id \op{asc}, Instant \op{asc}, Licence \op{asc}]\\
\>\op{krdup}[Id, Instant, Licence]\\
\op{let} Q15OBA =\\
\>QueryPoints1Net \op{feed projectextend}[Id, Pos; Prect:
\op{gpoint2rect}(.Pos)] \{p\}\\
\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))] \{t\}\\
\>\op{projectextend}[Id\_p, Pos\_p, Period\_t; Box: \op{box3d}(.Prect\_p,
.Period\_t)]\\
\>\op{loopsel} [\op{fun}(t:TUPLE) dataSNcar\_BoxNet\_timespace
\op{windowintersectsS}[attr(t, Box)]\\
\>\>\op{sort rdup} dataSNcar \op{gettuples}\\
\>\>\op{filter}[(.Trip \op{atperiods} (attr(t,Period\_t))) \op{passes}
(attr(t,Pos\_p))]\\
\>\>\op{projectextend}[; Id: attr(t,Id\_p), Period: attr(t,Period\_t), Licence:
.Licence]]\\
\>\op{sortby} [Id \op{asc}, Period \op{asc}, Licence \op{asc}]\\
\>\op{krdup} [Id, Period, Licence]\\
\op{let} Q15TBA =\\
\>QueryPoints1Net \op{feed projectextend} [Id, Pos; Prect:
\op{gpoint2rect}(.Pos)] \{p\}\\
\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{t\}\\
\>\op{loopsel}[\op{fun} (t:TUPLE) dataMNtrip\_BoxNet\_timespace
\op{windowintersectsS}[\\
\>\>\>\op{box3d}(attr(t,Prect\_p), attr(t,Period\_t))]\\
\>\>\op{sort rdup} dataMNtrip \op{gettuples}\\
\>\>\op{filter}[(.Trip \op{atperiods} (attr(t,Period\_t))) \op{passes}
(attr(t,Pos\_p))]\\
\>\>\op{projectextend} [Moid;Period: attr(t,Period\_t), Id:
attr(t,Id\_p)]]\{a\}\\
\>\op{loopjoin}[dataMcar\_Moid\_btree dataMcar \op{exactmatch} [.Moid\_a]]\\
\>\op{projectextend} [Licence; Id: .Id\_a, Period: .Period\_a]\\
\>\op{sortby} [Id \op{asc}, Period \op{asc}, Licence \op{asc}]\\
\>\op{krdup}[Id, Period, Licence]\\
\>\op{project}[Licence, Id, Period]\\
\op{let} Q16OBA =\\
\>\>\>\op{loopjoin} [dataSNcar\_Licence\_btree dataSNcar \op{exactmatch}
[.Licence\_l]] \{c\}\\
\>\>QueryPeriods1 \{op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\>\op{symmjoin}[.Trip\_c \op{present} ..Period\_p]\\
\>\>\>\op{projectextend}[Id\_p, Period\_p; Licence: .Licence\_c, Trip: .Trip\_c
\op{atperiods} .Period\_p]\\
\>\>\>\op{filter} [\op{no\_components}(.Trip) $>$ 0]\\
\>\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))] \{r\}\\
\>\>\op{symmjoin}[.Trip \op{passes} ..Region\_r]\\
\>\>\op{projectextend}[Licence, Id\_r, Region\_r, Id\_p, Period\_p; Trip: .Trip
\op{at} .Region\_r]\\
\>\>\op{filter}[\op{no\_components}(.Trip) $>$ 0]\{a\}\\
\>QueryLicences2 \op{feed} \{l\}\\
\>\>\>\op{loopjoin} [dataSNcar\_Licence\_btree dataSNcar \op{exactmatch}
[.Licence\_l]] \{c\}\\
\>\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\>\op{symmjoin} [.Trip\_c \op{present} ..Period\_p]\\
\>\>\>\op{projectextend}[Id\_p, Period\_p; Licence: .Licence\_c, Trip: .Trip\_c
\op{atperiods} .Period\_p]\\
\>\>\>\op{filter} [\op{no\_components}(.Trip) $>$ 0]\\
\>\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))]\{r\}\\
\>\>\op{symmjoin}[.Trip \op{passes} ..Region\_r]\\
\>\>\op{projectextend} [Licence, Id\_r, Region\_r, Id\_p, Period\_p; Trip: .Trip
\op{at} .Region\_r]\\
\>\>\op{filter} [\op{no\_components}(.Trip) $>$ 0]\{b\}\\
\>\op{symmjoin}[(.Id\_r\_a = ..Id\_r\_b) \op{and} (.Id\_p\_a = ..Id\_p\_b)]\\
\>\op{filter} [.Licence\_a $\neq$ .Licence\_b]\\
\>\op{filter} [\op{not}(.Trip\_a \op{intersects} .Trip\_b)]\\
\>\op{project} [Id\_r\_a, Period\_p\_a, Licence\_a, Licence\_b]\\
\op{let} Q16TBA =\\
\>\>\>\op{loopjoin} [dataMcar\_Licence\_btree dataMcar
\op{exactmatch}[.Licence\_l]] \{a\}\\
\>\>\>\op{loopjoin}[dataMNtrip\_Moid\_btree dataMNtrip
\op{exactmatch}[.Moid\_a]]\\
\>\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\>\op{symmjoin} [.Trip \op{present} ..Period\_p]\\
\>\>\>\op{projectextend}[Id\_p, Period\_p; Licence: .Licence\_a, Trip: .Trip
\op{atperiods} .Period\_p]\\
\>\>\>\op{filter}[\op{no\_components}(.Trip) $>$ 0]\\
\>\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))]\{r\}\\
\>\>\op{symmjoin} [.Trip \op{passes} ..Region\_r]\\
\>\>\>\op{projectextend}[Licence, Id\_p, Period\_p, Id\_r; Trip: .Trip \op{at}
.Region\_r]\\
\>\>\>\op{filter} [\op{no\_components} (.Trip) $>$ 0]\{a\}\\
\>QueryLicences2 \op{feed} \{l\}\\
\>\>\>\op{loopjoin} [dataMcar\_Licence\_btree dataMcar
\op{exactmatch}[.Licence\_l]]\{a\}\\
\>\>\>\op{loopjoin}[dataMNtrip\_Moid\_btree dataMNtrip
\op{exactmatch}[.Moid\_a]]\\
\>\>QueryPeriods1 \op{feed filter}[\op{not}(\op{isempty}(.Period))]\{p\}\\
\>\>\op{symmjoin} [.Trip \op{present} ..Period\_p]\\
\>\>\>\op{projectextend}[Id\_p, Period\_p; Licence: .Licence\_a, Trip: .Trip
\op{atperiods} .Period\_p]\\
\>\>\>\op{filter}[\op{no\_components}(.Trip) $>$ 0]\\
\>\>QueryRegions1Net \op{feed filter}[\op{not}(\op{isempty}(.Region))]\{r\}\\
\>\>\op{symmjoin} [.Trip \op{passes} ..Region\_r]\\
\>\>\>\op{projectextend}[Licence, Id\_p, Id\_r; Trip: .Trip \op{at}
.Region\_r]\\
\>\>\>\op{filter} [\op{no\_components} (.Trip) $>$ 0]\{b\}\\
